Responses to the Reviewers' Comments

### 2024-10-30 Response/Paper_Res.tex
Rev_V7.1

	\item \textbf{Affiliation}: $^\ast$ Department of Computer Engineering,  Sharif University of Technology, Tehran, Iran, \\ $^\dagger$ Department of Electrical Engineering, Sharif University of Technology, Tehran, Iran.

@@

\underline{Authors' Reply}: To address the reviewer comment, we have carefully studied the recently published papers and throughly revised the related work section. To be more specific,
\begin{enumerate}[]
\item We have devoted Section II of the revised manuscript to the literature review and provided a survey of the recently published state-of-the-art works.
\item Furthemore, we have expanded the explanations about each related work and discussed their pros/cons.
\end{enumerate}\vspace{6mm}
The newly added Section II of the revised manuscript is as follows. We have also included a table to provide a comprehensive comparison of the related works. \newline
\begin{my}{1cm}{1cm}
	\rev{\setcounter{section}{1}
\section{Related Work}
\label{section:II}
\,\,\,\,In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment.
		We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table1} provides an intuitive comparison of the related works.
	\subsection{DRL-based Computation Offloading for MEC}
	\,\,\,\,To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of RL in adapting to environmental changes and learning optimal strategies. To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
	Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
	Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading. 
	These works in \cite{huang2019deep}, \cite{liu2021learn} do not account for delay-sensitive tasks and may overlook critical performance factors in real-time applications. Besides, these studies \cite{huang2019deep}--\cite{zhou2021deep} primarily investigate simplified MEC networks, focusing on single MEC network models, considering only single-server or single-user scenarios, which may not always reflect real-world scenarios. 
	Moreover, due to the absence of robust underlying resource scheduling systems, issues such as data congestion during transmission and resource allocation can arise, leading to suboptimal system performance. Therefore, more accurate MEC models are needed to address the complexities of dynamic resource scheduling in large-scale scenarios. \vspace{2mm}

@@

	\item LSTM: Incorporating LSTM networks allows the model to continuously estimate dynamic workloads at edge servers. This feature is crucial for dealing with limited global information and adapting to an uncertain environment. By predicting the future workload of edge servers, mobile devices can effectively adjust their offloading strategies to achieve higher QoE.\vspace{2mm}

@@

To address the reviewer’s comment, we have further explained how the proposed algorithm enhances the performance of the computation offloading in MEC and specified the contributions. We have also highlighted the role of the LSTM network and its impact on the convergence and performance of the QECO algorithm. First, to further clarify our contributions, we have revised Section I as follows.

@@

Furthermore, to enhance the evaluation of our work, we have extended the performance analysis by comparing QECO with vanilla DQN and DDQN \cite{van2016deep}. This comparison illustrates the impacts of the LSTM network and dueling architecture. We have added Fig. 7 to Section V of the revised manuscript.

@@

\,\,\,\, To capture the interactions between agents and the environment, we carefully simulated an MEC system that allows the DRL agents to gain experience and generate the data required in the proper format for training. As the agent interacts with the environment, it generates new data at each time step, using the system’s feedback (e.g., QoE) to adjust its actions. As mentioned in Section III of the revised manuscript, based on queuing theory, our simulated model provides key system performance metrics (e.g., task delay, energy consumption, etc.), which enable the agent to determine the mobile device's QoE and evaluate each state-action advantage value.\vspace{2mm}

@@

(c) Indeed, QECO improves the number of completed tasks by 14.4\% while at the same time reduces task delay and energy consumption by 9.2\% and 6.3\%, respectively. These together contribute to a significant improvement by 37.1\% in average QoE compared to \cite{yang2018distributed}. To clarify the improvement obtained by QECO, we have revised the abstract, Section I, and Section VI as follows.

@@

\underline{Authors' Reply}: (a) We have carefully repaced the phrase "battery level" with "energy level" throughout the revised manuscript. \newline

@@

	\item \underline{Reviewer's Comment}: 
	\textit{``The authors should provide a comparative table to highlight their contributions. Specially, the authors should compare their method with other references on computation task offloading cited in the paper, including aspects such as scenarios, methods, advances, drawbacks, and so on.''} \newline

	\underline{Authors' Reply}: To address the reviewer's comment, we have carefully studied the recently published papers and revised the manuscript. 
	To be more specific, we have extended the literature review in Section II of the revised manuscript by providing a more comprehensive survey of the recently published state-of-the-art works and comparing their characteristics in Table \ref{table11}.
	We have also compared our work with more existing works and extended the performance evaluation in Section VI of the revised manuscript.

\vspace{3mm}
 The newly added Section II of the revised manuscript is as follows.

@@

We have extended the evaluation of the QECO algorithm by comparing it with DCDRL \cite{qiu2020distributed}, which is a distributed algorithm for delay-sensitive tasks based on the actor-critic framework. This is the foundation for many state-of-the-art DRL algorithms, including DDPG and PPO. We have added this comparison to Section VI of the revised manuscript as follows: 
\begin{my}{1cm}{1cm}
	\rev{
		{\
			\color{black}
			\hspace{-10mm}  \dots \\ We use the following methods as benchmarks.
			\begin{itemize}

@@

	\underline{Authors' Reply}: Given the importance of evaluating an agent's actions in DRL-based computation offloading approaches, we define the QoE maximization problem by considering several key performance factors. QoE is a time-varying performance measure that reflects user satisfaction and is influenced by more than just delay or energy consumption. On the other hand, investigating the trade-off between delay and energy consumption may not adequately address user demands and meet QoE requirements. To capture the agent’s personalized QoE needs, we designed an adaptive trade-off between task completion and cost reduction. In this model, the associated cost is a weighted sum of completion delay and energy consumption, with the weights dynamically adjusting based on the MD's preferences.\vspace{2mm}

@@

We have also revised the explanation related to Fig. 6 and Fig. 7 in Section VI of the revised manuscript to further specify how the QECO algorithm improves QoE for users. The following paragraph shows the changes we have made in Section VI of the revised manuscript.
		\begin{my}{1cm}{1cm}
	\rev{
		{\

@@

			\,\,\,\,  The algorithm's source code is available in \cite{QECO}.

@@

	\underline{Authors' Reply}: In response to the reviewer's comment, we have cited these works in the newly added related work section (i.e., Section II) and discussed their advantages and limitations. The following sentences reflect the changes we made in Section II of the revised manuscript.

>>>>

	\item \textbf{Affiliation}: $^\ast$Department of Computer Engineering,  Sharif University of Technology, Tehran, Iran, \\ $^\dagger$Department of Electrical Engineering, Sharif University of Technology, Tehran, Iran.

@@

\underline{Authors' Reply}: To address the reviewer comment, we have carefully studied the recently published papers and throughly revised the related work section. To be more specific,
\begin{enumerate}[]
\item We have devoted Section II of the revised manuscript to the literature review and provided a survey of the recently published state-of-the-art works.
\item Furthemore, we have expanded the explanations about each related work and discussed its pros/cons.
\end{enumerate}\vspace{6mm}
The newly added Section II of the revised manuscript is as follows. We have also included a table to provide a comprehensive comparison of the related works. \newline
\begin{my}{1cm}{1cm}
	\rev{\setcounter{section}{1}
\section{Related Work}
\label{section:II}
\,\,\,\,In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment.
		We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table~\ref{table1} provides an intuitive comparison of the related works.
	\subsection{DRL-based Computation Offloading for MEC}
	\,\,\,\,To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of RL in adapting to environmental changes and learning optimal strategies. To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
	Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
	Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading. 
	These works in \cite{huang2019deep}, \cite{liu2021learn} do not account for delay-sensitive tasks and may overlook critical performance factors in real-time applications. Besides, these studies \cite{huang2019deep}--\cite{zhou2021deep} primarily investigate simplified MEC networks, focusing on single MEC network models, considering only single-server or single-user scenarios, which may not always reflect real-world scenarios. 
	Moreover, due to the absence of robust underlying resource scheduling systems, issues such as data congestion during transmission and resource allocation can arise, leading to suboptimal system performance. Therefore, more accurate MEC models are needed to address the complexities of dynamic resource scheduling in large-scale scenarios. \vspace{2mm}

@@

	\item LSTM: Incorporating LSTM networks allows the model to continuously estimate dynamic workloads at edge servers. This is crucial for dealing with limited global information and adapting to the uncertain MEC environment with multiple MDs and ENs. By predicting the future workload of edge servers, MDs can effectively adjust their offloading strategies to achieve higher QoE.\vspace{2mm}

@@

To address the reviewer’s comment, we have further explained how the proposed algorithm enhances the performance of the computation offloading in MEC and specified our contributions. We have also highlighted the role of the LSTM network and its impact on the convergence and performance of the QECO algorithm. First, to further clarify our contributions, we have revised Section I as follows.

@@

@@

\,\,\,\, To capture the interactions between agents and the environment, we carefully simulated an MEC system that allows the DRL agents to gain experience and generate the data required in the proper format for training. As the agent interacts with the environment, it generates new data at each time step, using the system’s feedback (e.g., QoE) to adjust its actions.

%As mentioned in Section III of the revised manuscript, based on queuing theory, our simulated model provides key system performance metrics (e.g., task delay, energy consumption, etc.), which enable the agent to determine the mobile device's QoE and evaluate each state-action advantage value.\vspace{2mm}

@@

(c) Indeed, compared to \cite{yang2018distributed}, QECO improves the number of completed tasks by 14.4\% while at the same time reduces task delay and energy consumption by 9.2\% and 6.3\%, respectively. These together contribute to a significant improvement of 37.1\% in average QoE compared to \cite{yang2018distributed}. To clarify the improvement obtained by QECO, we have revised the abstract, Section I, and Section VI as follows.

@@

\underline{Authors' Reply}: (a) We have avoided using "battery level" to express the energy consumption and carefully repaced the phrase "battery level" with "energy level" throughout the revised manuscript. \newline

@@

	\item \underline{Reviewer's Comment}: 
	\textit{``(a) The authors should provide a comparative table to highlight their contributions. (b) Specially, the authors should compare their method with other references on computation task offloading cited in the paper, including aspects such as scenarios, methods, advances, drawbacks, and so on.''} \newline

	\underline{Authors' Reply}: (a) To address the reviewer's comment, we have carefully studied the recently published papers and revised the manuscript accordingly. 
	To be more specific, we have extended the literature review in Section II of the revised manuscript by providing a more comprehensive survey of the recently published state-of-the-art works and comparing their characteristics in Table \ref{table11}.
	We have also compared our work with more existing works and extended the performance evaluation in Section VI of the revised manuscript.

\vspace{3mm}
 The newly added Section II of the revised manuscript is as follows. As suggested by the reviewer, we have also included Table I that summarizes the existing works.

@@

We have extended the evaluation of the QECO algorithm by comparing it with DCDRL \cite{qiu2020distributed} in addition to POGA \cite{yang2018distributed}. DCDRL is a distributed algorithm for delay-sensitive tasks based on the actor-critic framework. This is the foundation for many state-of-the-art DRL algorithms, including DDPG and PPO. We have added this comparison to Section VI of the revised manuscript as follows: 
\begin{my}{1cm}{1cm}
	\rev{
		{\
			\color{black}
			\hspace{-10mm}  \dots \\ We use the following methods as benchmarks.
			\begin{itemize}

@@

	\underline{Authors' Reply}: Given the importance of evaluating an agent's action in DRL-based computation offloading approaches, we define the QoE maximization problem by considering several key performance factors. QoE is a time-varying performance measure that reflects user satisfaction and is influenced by more than just delay or energy consumption. On the other hand, investigating the trade-off between delay and energy consumption may not adequately address user demands and meet QoE requirements. To capture the agent’s personalized QoE needs, we designed an adaptive trade-off between task completion and cost reduction. In this model, the associated cost is a weighted sum of delay and energy consumption, with the weights dynamically adjusted based on the MD's preferences.\vspace{2mm}

@@

We have also revised the explanation related to Fig. 6 and Fig. 7 in Section VI of the revised manuscript to further specify how the QECO algorithm improves QoE of users. The following paragraph shows the changes we have made in Section VI of the revised manuscript.
		\begin{my}{1cm}{1cm}
	\rev{
		{\

@@

			\,\,\,\, The algorithm's source code is available at \cite{QECO}

@@

	\underline{Authors' Reply}: In response to the reviewer's comment, we have cited these works in the newly added related work section (i.e., Section II) and discussed their strengths and limitations. The following sentences reflect the changes we made in Section II of the revised manuscript.
